---
title: "Unit 1 - Exercise 1"
subtitle: "Repetition - Create report for data set struma"
author: "YOUR NAME"
date: "`r Sys.Date()`"
output: 
   html_document:
     toc: TRUE
     toc_float: TRUE
---

```{r setup, include = FALSE}
# settings for output
  knitr::opts_chunk$set(echo = FALSE)

# Change setting of figure width and height
  knitr::opts_chunk$set(fig.width = ggplot2::unit(10, "cm"), fig.height = ggplot2::unit(8, "cm"))


# libraries used in this Rmd
  library(ggplot2)
  library(tidyverse)
  library(flextable)
  library(gtsummary)
  
  library(cowplot)
```

```{r,  echo = FALSE, eval = TRUE}
# Load Rdata file
  filename <- list.files(path = "../Rdata/", pattern = "struma_prepared")

 load(file = paste0("../Rdata/", filename))

# show general information about dataset

 info$general %>% 
   flextable::flextable() %>% 
   flextable::font(., fontname = "Cambria (Textkörper)", part = "all") %>%
      flextable::fontsize(., size = 10 , part = "all") %>%
      flextable::padding(padding.top = 0,
                         padding.bottom = 0, part = "body") %>% 
  
      flextable::hline(.,
              border = officer::fp_border(color = "grey70", style = "dotted")) %>%
      # flextable::align(., j = 1, part = "all") %>%
      flextable::bg(., bg = "grey90", part = "header") %>% 
      flextable::bold(., bold = TRUE, part = "header") %>% 
      flextable::autofit()  

```

# Data set - struma

A goitre, or goiter, is a swelling in the neck resulting from an enlarged thyroid gland. 
[in German: goiter = Struma; goitre = Kropf].


In patients with goiter, a clinical study was conducted to investigate whether medication in addition to standard therapy (MED; yes/no) has an effect on thyroid hormones FT3, FT4 and TSH. 

## List of parameters
The data set contains following parameters

```{r, results = 'asis'}
mylist <- names(dt_struma)
cat(paste("-", mylist), sep = "\n")
```

## Information about parameters
```{r}
info$dictionary %>% 
   flextable::flextable() %>% 
   flextable::font(., fontname = "Cambria (Textkörper)", part = "all") %>%
      flextable::fontsize(., size = 10 , part = "all") %>%
      flextable::padding(padding.top = 0,
                         padding.bottom = 0, part = "body") %>% 
  
      flextable::hline(.,
              border = officer::fp_border(color = "grey70", style = "dotted")) %>%
      # flextable::align(., j = 1, part = "all") %>%
      flextable::bg(., bg = "grey90", part = "header") %>% 
      flextable::bold(., bold = TRUE, part = "header") %>% 
      flextable::autofit()  
```

# Descriptive statistics 
## Overview table
```{r}
# table with descriptive statistics
 # - look at arguments: 'included', 'by'
 # - hint for 'included': use negative sign ,e.g., '-c(test)'


 dt_struma %>%
  tbl_summary(by = MED) 

```

## Parameters
### gender

```{r, warning = FALSE}
# table 
 

```


```{r}
# bar plot - previous exercise
  # hint: try 'geom_bar(position=position_dodge())'


```



### age
```{r, warning = FALSE}
# table 


```

```{r}

# boxplot ---



# histogramm ---


# qq plot ---


# one big plot with panels
  # hint: cowplot::plot_grid(pA, pB, pC,plegend, nrow = 2, ncol = 2, labels = c("A", "B", "C", NA))

```

