---
title: "Unit 1 - Exercise 2"
subtitle: "Create report with placeholders"
author: "YOUR NAME"
date: "`r Sys.Date()`"
output: 
   html_document:
     toc: TRUE
     toc_float: TRUE
---

```{r setup, include = FALSE}
# settings for output
  knitr::opts_chunk$set(echo = FALSE)

# Change setting of figure width and height
  knitr::opts_chunk$set(fig.width = ggplot2::unit(10, "cm"), fig.height = ggplot2::unit(8, "cm"))


# libraries used in this Rmd
  library(ggplot2)
  library(tidyverse)
  library(flextable)
  library(gtsummary)
  
  library(cowplot)
```

```{r,  echo = FALSE, eval = TRUE}
# Load Rdata file
  filename <- list.files(path = "../Rdata/", pattern = "struma_prepared")

 load(file = paste0("../Rdata/", filename))

# show general information about dataset

 info$general %>% 
   flextable::flextable() %>% 
   flextable::font(., fontname = "Cambria (Textkörper)", part = "all") %>%
      flextable::fontsize(., size = 10 , part = "all") %>%
      flextable::padding(padding.top = 0,
                         padding.bottom = 0, part = "body") %>% 
  
      flextable::hline(.,
              border = officer::fp_border(color = "grey70", style = "dotted")) %>%
      # flextable::align(., j = 1, part = "all") %>%
      flextable::bg(., bg = "grey90", part = "header") %>% 
      flextable::bold(., bold = TRUE, part = "header") %>% 
      flextable::autofit()  

```

# Data set - struma

A goitre, or goiter, is a swelling in the neck resulting from an enlarged thyroid gland. 
[in German: goiter = Struma; goitre = Kropf].


In patients with goiter, a clinical study was conducted to investigate whether medication in addition to standard therapy (MED; yes/no) has an effect on thyroid hormones FT3, FT4 and TSH. 

## List of parameters
The data set contains following parameters

```{r, results = 'asis'}
mylist <- names(dt_struma)
cat(paste("-", mylist), sep = "\n")
```

## Information about parameters
```{r}
info$dictionary %>% 
   flextable::flextable() %>% 
   flextable::font(., fontname = "Cambria (Textkörper)", part = "all") %>%
      flextable::fontsize(., size = 10 , part = "all") %>%
      flextable::padding(padding.top = 0,
                         padding.bottom = 0, part = "body") %>% 
  
      flextable::hline(.,
              border = officer::fp_border(color = "grey70", style = "dotted")) %>%
      # flextable::align(., j = 1, part = "all") %>%
      flextable::bg(., bg = "grey90", part = "header") %>% 
      flextable::bold(., bold = TRUE, part = "header") %>% 
      flextable::autofit()  
```

# Descriptive statistics 
```{r}
# placeholders
group_int <- "MED"
group_int_lab <- "Medication"
group_int_colors <- c("#00AFBB", "#E7B800")

```

## Overview table
```{r, include = FALSE}
## SOLUTION previous exercise ##

# # table with descriptive statistics
#  dt_struma %>%
#   tbl_summary(include = -c(PatId),
#               by = MED,
#               statistic = list(where(is.numeric) ~  "{mean} ({sd})")) %>% 
#   bold_labels() %>% 
#   modify_spanning_header(all_stat_cols() ~ "**Medication**") 

```

```{r}
# table 
# hint: 
#  1) we need to replace MED with group_int
#  2) we need to adapt "**Medication**" - use: paste0("**", group_int_lab, "**")
 
```


## Parameters
### gender
```{r}
# placeholders
var_int <- "gender"
var_int_lab <- "Gender"
```

```{r, include = FALSE}
## SOLUTION previous exercise ##

# # table 
#  dt_struma %>%
#   tbl_summary(include = gender,
#               by = MED,
#               statistic = list(where(is.numeric) ~  "{mean} ({sd})")) %>% 
#   bold_labels() %>% 
#   modify_spanning_header(all_stat_cols() ~ "**Medication**") 

```

```{r, warning = FALSE}
# table 
# hint: 
#  1) we need to replace gender with all_of(var_int)
#  2) we need to replace MED with group_int
#  3) we need to adapt "**Medication**" - use: paste0("**", group_int_lab, "**")

 
```


```{r, include = FALSE}
## SOLUTION previous exercise ##

# # bar plot - previous exercise
# 
# ggplot(data = dt_struma,
#        aes(x = gender, fill = MED)) +
#   geom_bar(position=position_dodge()) +
#    scale_fill_manual(values = c("#00AFBB", "#E7B800")) +
#     theme_bw() +
#     theme(legend.position = "bottom")

```

```{r}
# Hint: for ggplot you need to use
# get(var_int) and get(group_int) in aes()

# bar plot

```



### age
```{r}
# placeholders
var_int <- "age"
var_int_lab <- "Age [years]"
```

```{r, include = FALSE}
## SOLUTION previous exercise ##

# # table 
 # dt_struma %>%
 #  tbl_summary(include = age,
 #              by = MED,
 #              type = list(age ~ "continuous2"),
 #              statistic = list(all_continuous2() ~ c("{median} ({p25} - {p75})",
 #                                                   "{min} - {max}",
 #                                                   "{mean} ({sd})"))) %>%
 #  bold_labels() %>%
 #   modify_spanning_header(all_stat_cols() ~ "**Medication**")

```

```{r, warning = FALSE}
# table

```


```{r, include = FALSE}
## SOLUTION previous exercise ##

# # boxplot ---
# p_boxplot <- 
# ggplot(data = dt_struma,
#        aes(x = age, fill = MED)) +
#   geom_boxplot() +
#   scale_fill_manual(values = c("#00AFBB", "#E7B800")) +
#     theme_bw()+
#     theme(legend.position = "bottom")
# 
# 
# # histogramm ---
# p_hist <- 
# ggplot(data = dt_struma,
#        aes(x = age, fill = MED)) +
#   geom_histogram(color = "black") +
#   scale_fill_manual(values = c("#00AFBB", "#E7B800")) +
#    theme_bw()+
#    theme(legend.position = "bottom") +
# 
#   facet_grid(MED~.)
# 
# # qq plot ---
# p_qqplot <-
# ggplot(data = dt_struma,
#        aes(sample = age, color = MED)) +
#   geom_qq() +
#   geom_qq_line() +
# 
#     xlab("Theoretical") +
#     ylab("Sample") +
#     scale_color_manual(values = c("#00AFBB", "#E7B800")) +
#   theme_bw() +
# 
#   facet_grid(MED~.)
# 
# # one big plot with panels
# 
# pA <- p_boxplot + theme(legend.position = "none")
# pC <- p_hist + theme(legend.position = "none")
# pB <- p_qqplot + theme(legend.position = "none")
# 
# 
# plegend <-  cowplot::get_legend(p_boxplot) #cowplot::get_plot_component(plot, 'guide-box-top', return_all = TRUE) 
# 
# cowplot::plot_grid(pA, pB, pC,plegend, nrow = 2, ncol = 2, labels = c("A", "B", "C", NA))

```

```{r}
# Hint: for ggplot you need to use
# get(var_int) and get(group_int) in aes()

# boxplot ---


  
# histogramm ---



# qq plot ---


# one big plot with panels


```


### blood group



### weight
