---
title: "Unit 2 - Exercise 1 (SOLUTION)"
subtitle: "Example struma"
author: "YOUR NAME"
date: "`r Sys.Date()`"
output: 
   html_document:
     toc: TRUE
     toc_float: TRUE
---

```{r setup, include = FALSE}
# settings for output
  knitr::opts_chunk$set(echo = FALSE)

  knitr::opts_chunk$set(warning = FALSE ) # check once all warnings and if you want to ignore them set here "FALSE

 knitr::opts_chunk$set(message = FALSE ) # if you want to ignore the comments written by functions, e.g. "`stat_bin()` using `bins = 30`."

  
# Change setting of figure width and height
  knitr::opts_chunk$set(fig.width = ggplot2::unit(10, "cm"), fig.height = ggplot2::unit(8, "cm"))

# Change options such that progress bar is not shown in the output file <- NEW!!!
  knitr::opts_knit$set(progress = FALSE, verbose = TRUE)

# libraries used in this Rmd
  library(ggplot2)
  library(tidyverse)
  library(flextable)
  library(gtsummary)
  library(knitr)
  
  library(cowplot)
```

```{r,  echo = FALSE, eval = TRUE}
# Load Rdata file
  filename <- list.files(path = "../Rdata/", pattern = "struma_prepared")

 load(file = paste0("../Rdata/", filename))

# show general information about dataset

 info$general %>% 
   
   flextable::flextable() %>% 
   flextable::font(., fontname = "Cambria (Textkörper)", part = "all") %>%
      flextable::fontsize(., size = 10 , part = "all") %>%
      flextable::padding(padding.top = 0,
                         padding.bottom = 0, part = "body") %>% 
  
      flextable::hline(.,
              border = officer::fp_border(color = "grey70", style = "dotted")) %>%
      # flextable::align(., j = 1, part = "all") %>%
      flextable::bg(., bg = "grey90", part = "header") %>% 
      flextable::bold(., bold = TRUE, part = "header") %>% 
      flextable::autofit()  

```

We will use 'knit_child()' to call `subroutine` Rmd file.


# Data set - struma

A goitre, or goiter, is a swelling in the neck resulting from an enlarged thyroid gland. 
[in German: goiter = Struma; goitre = Kropf].


In patients with goiter, a clinical study was conducted to investigate whether medication in addition to standard therapy (MED; yes/no) has an effect on thyroid hormones FT3, FT4 and TSH. 

## List of parameters
The data set contains following parameters

```{r, results = 'asis'}
mylist <- names(dt_struma)
cat(paste("-", mylist), sep = "\n")
```

## Information about parameters
```{r}
info$dictionary %>% 
   flextable::flextable() %>% 
   flextable::font(., fontname = "Cambria (Textkörper)", part = "all") %>%
      flextable::fontsize(., size = 10 , part = "all") %>%
      flextable::padding(padding.top = 0,
                         padding.bottom = 0, part = "body") %>% 
  
      flextable::hline(.,
              border = officer::fp_border(color = "grey70", style = "dotted")) %>%
      # flextable::align(., j = 1, part = "all") %>%
      flextable::bg(., bg = "grey90", part = "header") %>% 
      flextable::bold(., bold = TRUE, part = "header") %>% 
      flextable::autofit()  
```

# Descriptive statistics 
```{r}
# placeholders
dt_analysis <- dt_struma

group_int <- "MED"
group_int_lab <- "Medication"
group_int_colors <- c("#00AFBB", "#E7B800")

vec_var_int_categorical <- c("gender", "bloodgrp", "smoking")
vec_var_int_categorical_lab <- c("Gender", "Blood group", "Smoking level")
  
vec_var_int_continuous <- c('systbp', 'weight', 'weight_1year', 'height', 'abd_grith',
                            'hip_size', 'FT3', 'FT4', 'TSH', 'age')
vec_var_int_continuous_lab <- c('systolic blood pressure [mmHg]', 'weight [kg]', 'weight after 1 year [kg]', 'height [cm]', 'abdominal grith [cm]', 
                                'hip size [cm]', 'FT3', 'FT4', 'TSH', 'age [years]')
```

## Overview table
```{r}
# NEW: change to have more information for continious parameters with 'continuous2'

 dt_analysis %>%
  tbl_summary(include = -all_of(c("PatId")),
              by = all_of(group_int),
              type = list(where(is.numeric) ~ "continuous2"), 
              statistic = list(all_continuous() ~  c("{median} ({p25}, {p75})", "{mean} ({sd})"),
                               where(is.POSIXct) ~  "{median} ({min}, {max})")) %>% 
  bold_labels() %>% 
  modify_spanning_header(all_stat_cols() ~ paste0("**", group_int_lab, "**")) 

```

## Categorical parameters - no loop

```{r, results = 'asis'}
# for categorical parameters

var_int <- "gender"
var_int_lab <- "Gender"


cat(knit_child("0_subRmds/subRmd_categorical_withgroup_SOLUTION_v20250304.Rmd"), sep = '\n')


```


## Continuous parameters - no loop

```{r, results = 'asis'}
# for continuous parameters

var_int <- 'systbp'
var_int_lab <- 'systolic blood pressure [mmHg]'


cat(knit_child("0_subRmds/subRmd_continuous_withgroup_SOLUTION_v20250304.Rmd"), sep = '\n')


```


## Categorical parameters - with loop

```{r, results = 'asis'}
# for loop for categorical parameters

for (j in 1:length(vec_var_int_categorical)) {
# for (j in 2:2) {

   var_int <- vec_var_int_categorical[j]
   var_int_lab<- vec_var_int_categorical_lab[j]

   cat(knit_child("0_subRmds/subRmd_categorical_withgroup_SOLUTION_v20250304.Rmd"), sep = '\n')


  rm(var_int, var_int_lab)
 }

``` 

## Continuous parameters - with loop

```{r, results = 'asis'}
# for loop for continuous parameters

for (j in 1:length(vec_var_int_continuous)) {
# for (j in 1:3) {

   var_int <- vec_var_int_continuous[j]
   var_int_lab<- vec_var_int_continuous_lab[j]

   cat(knit_child("0_subRmds/subRmd_continuous_withgroup_SOLUTION_v20250304.Rmd"), sep = '\n')


  rm(var_int, var_int_lab)
 }

```



## Continuous parameters - with tabs {.tabset}

```{r, results = 'asis'}
# for loop for continuous parameters

#for (j in 1:length(vec_var_int_continuous)) {
 for (j in 1:3) {

   var_int <- vec_var_int_continuous[j]
   var_int_lab<- vec_var_int_continuous_lab[j]

   cat(knit_child("0_subRmds/subRmd_continuous_withgroup_SOLUTION_v20250304.Rmd"), sep = '\n')


  rm(var_int, var_int_lab)
 }

```


