---
title: "Unit4 - Exercise 1"
subtitle: "Example wide/long format"
author: "YOUR NAME"
date: "`r Sys.Date()`"
output: 
   html_document:
     toc: TRUE
     toc_float: TRUE
---

```{r setup, include = FALSE}
# settings for output
  knitr::opts_chunk$set(echo = FALSE)


# Change setting of figure width and height
  knitr::opts_chunk$set(fig.width = ggplot2::unit(10, "cm"), fig.height = ggplot2::unit(8, "cm"))

# Change options such that progress bar is not shown in the output file <- NEW!!!
  knitr::opts_knit$set(progress = FALSE, verbose = TRUE)

# libraries used in this Rmd
  library(ggplot2)
  library(tidyverse)
  library(flextable)
  library(gtsummary)
  library(knitr)
  
  library(cowplot)
```


# Example 1: use pivot_longer()
Suppose we have the following data frame in R that shows the systolic blood pressure by various patients at different days

```{r,  echo = TRUE, eval = TRUE}
# Create data
  dt_study <-
    tibble(patient  = paste0("P", 1:5),
           age = c(33, 46, 27, 59, 33),
           sysbp1 = c(100, 85, 99, 76, 103),
           sysbp2 = c(101, 86, 85, 76, 99),
           sysbp3 = c(89, 88, 79, 83, 99))
```

We can use the pivot_longer() function to pivot this data frame into a long format.

```{r,  echo = TRUE, eval = TRUE}
# pivot the data frame into a long format (save it as dt_study_long)
 # hint: look at arguments 'names_to' and 'values_to' 
 #       such that in the end your column headers are
 #        patient, age, measurement, systbp


```

```{r,  echo = TRUE, eval = TRUE}
# Look at dt_study_long

```

```{r,  echo = TRUE, eval = TRUE}
# plot systolic blood pressure and measuremnt with ggplot and geom_line()
  # hint: you need to have in aes(..., group = patient)
  #       try also to have colour related to parameter patient

```

# Example 2: use pivot_longer()
Suppose we have the same dataset as in example 1 but with the additional information of dates

```{r,  echo = TRUE, eval = TRUE}
# Create data
  dt_study2 <-
    tibble(patient  = paste0("P", 1:5),
           age = c(33, 46, 27, 59, 33),
           sysbp1 = c(100, 85, 99, 76, 103),
           sysbp2 = c(101, 86, 85, 76, 99),
           sysbp3 = c(89, 88, 79, 83, 99),
           date1 = as.Date(x = paste0(c(10, 13, 9, 12, 22), ".04.2022"), format = "%d.%m.%Y"),
           date2 = as.Date(x = paste0(c(11, 15, 11, 13, 23), ".04.2022"), format = "%d.%m.%Y"),
           date3 = as.Date(x = paste0(c(12, 16, 14, 14, 24), ".04.2022"), format = "%d.%m.%Y"))
```


We can use again the pivot_longer() function to pivot this data frame into a long format.

```{r,  echo = TRUE, eval = TRUE}
# pivot the data frame into a long format (save it as dt_study2_long)
 # hint: you will need two separate pivot_longer calls, one for each new column you want to create
 # hint; copy code for dt1 and adapt it to get dt2 with the dates instead of systbp
 #  if dt1 and dt2 work use code which is currently in comments (use ?left_join to see what this function does)

dt1 <-
   dt_study2 %>% 
    select(patient, age, sysbp1, sysbp2, sysbp3) %>% 
    pivot_longer(cols = c(sysbp1, sysbp2, sysbp3),
                 names_to = "measurement",
                 values_to = "systbp") %>% 
   mutate(measurement = str_remove(string = measurement, pattern = "sysbp"))


 
   
 # dt_study2_long <-
 #   left_join(x = dt1,
 #             y = dt2,
 #             by = c("patient" = "patient",
 #                    "age" = "age",
 #                    "measurement" = "measurement"))

```

```{r,  echo = TRUE, eval = TRUE}
# Look at dt_study2_long

```

```{r,  echo = TRUE, eval = TRUE}
# plot systolic blood pressure and dates with ggplot and geom_line()
  # hint: you need to have in aes(..., group = patient)
  #       try also to have colour related to parameter patient
  # hint: set the scale limits for y-axis such that you can see values between 75 and 125


```


# Example 3: use pivot_wider()
Suppose we have the following data frame in R that contains information about various basketball players

```{r,  echo = TRUE, eval = TRUE}
# Create data
  dt_game <-
    tibble(player = rep(c('A', 'B'), each = 4),
           bloodgroup = rep(c('A', 'AB'), each = 4),
           year = rep(c(1, 1, 2, 2), times = 2),
           stat = rep(c('points', 'assists'), times=4),
           amount = c(14, 6, 18, 7, 22, 9, 38, 4))
```

We can use the pivot_wider() function to pivot this data frame into a wide format

```{r,  echo = TRUE, eval = TRUE}
# pivot the data frame into a wide format (save it as dt_game_wide)
 # hint: look at arguments 'names_from' and 'values_from' 
 #       such that in the end your column headers are
 #        player, bloodgroup,  year, points, assists

 
```

```{r,  echo = TRUE, eval = TRUE}
# Look at dt_game_wide

```


# Example 4: struma
Load struma dataset 

* create a long format version using the parameters: PatId, bloodgrp, weight, and weight_1year
* plot weight with the two measurements and colour the lines according to the bloodgroup
```{r,  echo = FALSE, eval = TRUE}
# Load struma Rdata file
  
```


```{r,  echo = TRUE, eval = TRUE}
# pivot the data frame into a long format (save it as dt_struma_long)

# hint: work first with select() before you use pivot_longer()
 #      we will need only: PatId, bloodgrp, weight, weight_1year
 


```


```{r,  echo = TRUE, eval = TRUE}
# plot sweight and measuremnt with ggplot and geom_line()
  # hint: you need to have in aes(..., group = patient)
  #       try also to have colour related to parameter bloodgroup


```