---
title: "Unit4 - Exercise 4 (SOLUTION)"
subtitle: "Example functions"
author: "YOUR NAME"
date: "`r Sys.Date()`"
output: 
   html_document:
     toc: TRUE
     toc_float: TRUE
---

```{r setup, include = FALSE}
# settings for output
  knitr::opts_chunk$set(echo = FALSE)


# Change setting of figure width and height
  knitr::opts_chunk$set(fig.width = ggplot2::unit(10, "cm"), fig.height = ggplot2::unit(8, "cm"))

# Change options such that progress bar is not shown in the output file <- NEW!!!
  knitr::opts_knit$set(progress = FALSE, verbose = TRUE)

# libraries used in this Rmd
  library(ggplot2)
  library(tidyverse)
  library(flextable)
  library(gtsummary)
  library(knitr)
  
  library(cowplot)
```


# Example 1: x + y
* Write a function in which the two numbers are added and the resulting sum will be returned

```{r,  echo = TRUE, eval = TRUE}
# function for x+y
  sum_two_nums <- function(x, y){
    return(x + y)
   } 
```

* Test your function with x = 2 and y = 4

```{r,  echo = TRUE, eval = TRUE}
  sum_two_nums(x = 2, y = 4)
```

* add default values: x = 0 and y = 100

```{r,  echo = TRUE, eval = TRUE}
# function for x+y with default values 
  sum_two_nums_new <- function(x = 0, y = 100){
    return(x + y)
   } 
```

* Test your updated function with x = 12 and give no value for y
```{r,  echo = TRUE, eval = TRUE}
  sum_two_nums_new(x = 12)
```

* Test your updated function with y = 3 and give no value for x
```{r,  echo = TRUE, eval = TRUE}
  sum_two_nums_new(y = 12)
```

# Example 2:  mean_median()
* Write a function which returns mean and median of a vector with values using built-in functions
```{r,  echo = TRUE, eval = TRUE}
# function which returns mean and median
  # hint: for return() you can use a vector as an object which should be returned

  mean_median <- function(vector){
    mean <- mean(vector)
    median <- median(vector)
    return(c(mean = mean, median = median))
} 
```


* Test your function with c(1, 3, 44, 2)

```{r,  echo = TRUE, eval = TRUE}
  mean_median(vector = c(1, 3, 44, 2))
```


# Link
Look at https://bookdown.org/content/d1e53ac9-28ce-472f-bc2c-f499f18264a3/func.html to get further information.