---
title: "Unit3 - Exercise 1"
subtitle: "Example struma - simple linear regression"
author: "YOUR NAME"
date: "`r Sys.Date()`"
output: 
   html_document:
     toc: TRUE
     toc_float: TRUE
---

```{r setup, include = FALSE}
# settings for output
  knitr::opts_chunk$set(echo = FALSE)


# Change setting of figure width and height
  knitr::opts_chunk$set(fig.width = ggplot2::unit(10, "cm"), fig.height = ggplot2::unit(8, "cm"))

# Change options such that progress bar is not shown in the output file <- NEW!!!
  knitr::opts_knit$set(progress = FALSE, verbose = TRUE)

# libraries used in this Rmd
  library(ggplot2)
  library(tidyverse)
  library(flextable)
  library(gtsummary)
  library(knitr)
 
  
  library(cowplot)
```

```{r,  echo = FALSE, eval = TRUE}
# Load Rdata file
  filename <- list.files(path = "../Rdata/", pattern = "struma_prepared")

 load(file = paste0("../Rdata/", filename))

# show general information about dataset

 info$general %>% 
   flextable::flextable() %>% 
   flextable::font(., fontname = "Cambria (Textkörper)", part = "all") %>%
      flextable::fontsize(., size = 10 , part = "all") %>%
      flextable::padding(padding.top = 0,
                         padding.bottom = 0, part = "body") %>% 
  
      flextable::hline(.,
              border = officer::fp_border(color = "grey70", style = "dotted")) %>%
      # flextable::align(., j = 1, part = "all") %>%
      flextable::bg(., bg = "grey90", part = "header") %>% 
      flextable::bold(., bold = TRUE, part = "header") %>% 
      flextable::autofit()  

```


**TO DO**

* Investigate the following question
   - What is the relationship between weight ('weight') and systolic blood pressure ('systbp'), respectively can weight explain systolic blood pressure?
      + There is an update regarding one patient: PatId 100 has weight of 70kg not 55kg
* Check the different assumptions
   - hints will be given within the chunks
* Look at R package 'moderndive'


# Linear regression analysis
```{r, echo = TRUE}
# Adapt entry of patient PatId 100
  dt_analysis <-
    dt_struma %>% 
      mutate(weight = ifelse(PatId == "100", 70, weight))
```

## Scatterplot
```{r, echo = TRUE}
# scatterplot with ggplot and geom_point

  # xlab with "Weight [kg]"
  # ylab with "Syst BP [mmHg]"

ggplot(data = dt_analysis,
       aes(x = weight, y = systbp)) +
  geom_point() +
  
  xlab("Weight [kg]") +
  ylab("Syst BP [mmHg]") +
  
  theme_bw()
```


## Model
```{r, echo = TRUE}
# simple linear regression model using function lm()
 # save model result on 'res_model'
  res_model <- lm(formula = systbp ~ weight,
                  data = dt_analysis )
```

### Results - console output
```{r, echo = TRUE}
# print console output by printing res_model 
 res_model
 
```

```{r, echo = TRUE}
# print console output by using summary(res_model)
  summary(res_model)
 
```

## Model assumptions
* **Independence** - through study design
* **Linearity** - scatter plot above

### Residuals
```{r, echo = TRUE}
# Create dataset 'dt_fit_pred' with: observed weight, systbp, fitted values and standardized fitted values, residuals and standardized residuals
 # hint: look what happens if you type in console res_model$
 # hint: for standardized residuals use function rstandard()
 # hint: for standardized fitted values; fit_value_stand = (fit_value - mean(fit_value))/sd(fit_value)

dt_fit_pred <-
   res_model$model %>%  
   as_tibble() %>% 
   mutate(fit_value = res_model$fitted.values,
          fit_value_stand = (fit_value - mean(fit_value))/sd(fit_value),
          residuals = res_model$residuals,
          residuals_stand = rstandard(res_model))
 
```

#### Check normality assumption for residuals
```{r, echo = TRUE}
# Plot a 2x1 plot to check normality assumption for residuals (use plot_grid() from package cowplot))
  # panel A: histogram
  # panel B: qqplot

p_res_stand<-
  ggplot(data = dt_fit_pred,
         aes(x = residuals_stand)) +
    geom_histogram(fill = "grey80", colour = "black") +
    xlab("Standardized Residual") +
    theme_bw()


p_res_qqplot <-
  ggplot(data = dt_fit_pred,
         aes(sample = residuals_stand)) +
    geom_qq() +
    geom_qq_line() +
  
      xlab("Theoretical") +
      ylab("Standardized Residual") +
    theme_bw()

cowplot::plot_grid(p_res_stand, p_res_qqplot, nrow = 2)

```

#### Check homoscedasticity assumption
```{r, echo = TRUE}

        
  ggplot(data = dt_fit_pred,
         aes(x = fit_value_stand, y = residuals_stand)) +
        
          geom_point(fill = "grey80", colour = "black") +
          ylab("Standardized residuals") +
          xlab("Standardized fitted values") +
          theme_bw() +
        theme(axis.title = element_text(size = 15),
              axis.text = element_text(size = 13),
              legend.position = "none")
```

## Model plot
```{r, echo = TRUE}
# scatterplot with regression line
 # hint: use for line: geom_line(data = dt_fit_pred, ...)

ggplot(data = dt_analysis,
       aes(x = weight, y = systbp)) +
  geom_point() +
  
  geom_line(data = dt_fit_pred ,
              aes(x = weight,
                  y = fit_value )) +
  
  xlab("Weight [kg]") +
  ylab("Syst BP [mmHg]") +
  
  theme_bw()

```

## Model plot with uncertainty
```{r, echo = TRUE}
# scatterplot with regression line + uncertainty
 # hint: create a 'dt_pred' with predictions using function predict() 
 #       for argument 'newdata' use tibble(weight = seq(from, to, by))

 # hint: for plot geom_ribbon() and geom_line() use 'data = dt_pred' and for geom_point() 'data = dt_analysis' 
  

weight_new <- seq(from = min(dt_analysis$weight),
                  to = max(dt_analysis$weight),
                  by = 0.5)

dt_pred <-
  predict(object = res_model,
          newdata = tibble(weight = weight_new),
          interval = "confidence",
          level = 0.95) %>%
  as_tibble() %>%
  bind_cols(weight = weight_new, .)


ggplot() +
  geom_ribbon(data = dt_pred,
              aes(x = weight_new,
                  y = fit,
                  ymin = lwr,
                  ymax = upr),
              fill = "lightgrey") +
  geom_line(data = dt_pred,
              aes(x = weight_new,
                  y = fit)) +

  geom_point(data = dt_analysis,
             aes(x = weight, y = systbp),
             alpha = 0.8, colour = "darkred") +

  xlab("Weight [kg]") +
  ylab("Syst BP [mmHg]") +

  theme_bw()



```




## Useful package 'moderndive'
Details on https://moderndive.github.io/moderndive/


```{r, echo = TRUE}
# 1) Install package: install.packages("moderndive") <- only once or via munue Tools/Install Packages
# 2) load library: library(moderndive)

library(moderndive)
```

### Regression table with confidence intervals
```{r, echo = TRUE}
# hint: use flextable (see code in second junk)
#       optional: to change digits for column 'XXX' us: flextable::colformat_double(., j = "XXX", digits = 3)

get_regression_table(res_model) %>% 
   flextable::flextable() %>% 
  
   flextable::colformat_double(., j = "p_value", digits = 3)  %>% 
  
   flextable::font(., fontname = "Cambria (Textkörper)", part = "all") %>%
      flextable::fontsize(., size = 10 , part = "all") %>%
      flextable::padding(padding.top = 0,
                         padding.bottom = 0, part = "body") %>% 
  
      flextable::hline(.,
              border = officer::fp_border(color = "grey70", style = "dotted")) %>%
      flextable::bg(., bg = "grey90", part = "header") %>% 
      flextable::bold(., bold = TRUE, part = "header") %>% 
      flextable::autofit() 
```

### Fitted/predicted values and residuals
Get information on each point/observation in your regression, including fitted/predicted values and residuals, in a single data frame
```{r, echo = TRUE}
# save it to 'dt_fit_pred_new'
# hint: use flextable to print table

dt_fit_pred_new <- get_regression_points(res_model)

dt_fit_pred_new %>% 
  head() %>% 
  flextable::flextable() %>% 
  
  # flextable::colformat_double(., j = "p_value", digits = 3)  %>% 
  
   flextable::font(., fontname = "Cambria (Textkörper)", part = "all") %>%
      flextable::fontsize(., size = 10 , part = "all") %>%
      flextable::padding(padding.top = 0,
                         padding.bottom = 0, part = "body") %>% 
  
      flextable::hline(.,
              border = officer::fp_border(color = "grey70", style = "dotted")) %>%
      flextable::bg(., bg = "grey90", part = "header") %>% 
      flextable::bold(., bold = TRUE, part = "header") %>% 
      flextable::autofit() 

```


### Summaries of regression fit 
```{r, echo = TRUE}
# hint: use flextable to print table 

get_regression_summaries(res_model) %>% 
  flextable::flextable() %>% 
  
   flextable::colformat_double(., j = "p_value", digits = 3)  %>% 
  
   flextable::font(., fontname = "Cambria (Textkörper)", part = "all") %>%
      flextable::fontsize(., size = 10 , part = "all") %>%
      flextable::padding(padding.top = 0,
                         padding.bottom = 0, part = "body") %>% 
  
      flextable::hline(.,
              border = officer::fp_border(color = "grey70", style = "dotted")) %>%
      flextable::bg(., bg = "grey90", part = "header") %>% 
      flextable::bold(., bold = TRUE, part = "header") %>% 
      flextable::autofit() 

```





* $R^2$ - proportion of variance in the data that is explained by the model
* $R^2_{adj}$ - $R^2$ with penalizing the addition of 'unnecessary' variables
* MSE (mean squared error) - measures the average of the squares of the errors
* RMSE (root mean square error) - measures the average difference between a statistical model's predicted values and the actual values
* sigma - residual standard deviation
* statistic - is the F-statistic value of the model; ratio of two variances (variance explained by the parameters in the model/unexplained variance)
* p_value - probability of achieving an F-statistic that large under the null hypothesis of no effect
   - $H_0:$ all coefficients in the model are equal to zero
   - $H_A:$ not every coefficient is simultaneously equal to zero
* df (degree of freedom)  - console output more informative
* nobs - number of observations used in the model

