---
title: "Unit4 - Exercise 3"
subtitle: "Example join data sets"
author: "YOUR NAME"
date: "`r Sys.Date()`"
output: 
   html_document:
     toc: TRUE
     toc_float: TRUE
---

```{r setup, include = FALSE}
# settings for output
  knitr::opts_chunk$set(echo = FALSE)


# Change setting of figure width and height
  knitr::opts_chunk$set(fig.width = ggplot2::unit(10, "cm"), fig.height = ggplot2::unit(8, "cm"))

# Change options such that progress bar is not shown in the output file <- NEW!!!
  knitr::opts_knit$set(progress = FALSE, verbose = TRUE)

# libraries used in this Rmd
  library(ggplot2)
  library(tidyverse)
  library(flextable)
  library(gtsummary)
  library(knitr)
  
  library(cowplot)
```


# Join data sets
We work with different data sets about patients

```{r}
# create data
## Data set 1
dt_death <- tibble( PatientID  = c('P001','P002','P003'),
                    Age           = c(23,12,5),
                    Outcome    = c('Died','Died',NA)   )

## Data set 2
dt_bp <- tibble(PatientID   = c('P001','P002','P004'),
                    SBP       = c(120,    80, 45),
                    DBP       = c(80,    70, 30)
 )

## Data set 3
dt_weight <- tibble(PatientID   = c('P001','P005','P006'),
                        Weight   = c(80, 65, 78)
)

## Data set 4
dt_hr <- tibble(PatID   = c('P001','P004','P007')
                   , HeartRate   = c(65, 65, 72)
)

```


## Data sets

- Have a quick look at the data sets to get an idea about the content

```{r}

```


## Join - *inner_join*

* **inner_join**: only keeps observations from x that have a matching key in y
   - test it with 'dt_death' and 'dt_bp'

```{r, echo = TRUE, eval = TRUE}
 
```

- For how many patients you still have data entries?

## Join - *full_join*

* **full_join**: keeps all observations in x and y
    - test it with 'dt_death' and 'dt_bp'

```{r, echo = TRUE, eval = TRUE}
 
 
```


- Check the difference to 'inner_join()'

## Join - *left_join*

* **left_join**:   keeps all observations in x
   - test it with 'dt_death' and 'dt_hr'

```{r, echo = TRUE, eval = TRUE}
 

```

## Join - *right_join*

* **right_join**:   keeps all observations in y
      - test it with 'dt_death' and 'dt_hr'

```{r, echo = TRUE, eval = TRUE}
 
 
```


- Do you see the difference to 'left_join'?


## Join - with two keys
```{r, echo = TRUE, eval = TRUE}
 dt_pat <-
   tibble(PatID = c(paste0('P00', c(1:10))),
          sex   = c("m", "m", "m", "f", "f",
                              "m", "f", "m", "m", "f"),
          medication = c(rep("A", 5), rep("B", 5)),
          center = rep(c("c1", "c2"), 5))

dt_center <-
  tibble(center = c("c1", "c1", "c2", "c2"),
         medi = c("A", "B", "B", "A"),
         checkup = c("today", "tomorrow", "never", "next week")
  )

 
```

- Look at the data sets

```{r}

```


- Add to the patient data set when the next check-up should take place


```{r, echo = TRUE, eval = TRUE}
 
 
 
```