---
title: "Unit4 - Exercise 2"
subtitle: "Example group_by"
author: "YOUR NAME"
date: "`r Sys.Date()`"
output: 
   html_document:
     toc: TRUE
     toc_float: TRUE
---

```{r setup, include = FALSE}
# settings for output
  knitr::opts_chunk$set(echo = FALSE)


# Change setting of figure width and height
  knitr::opts_chunk$set(fig.width = ggplot2::unit(10, "cm"), fig.height = ggplot2::unit(8, "cm"))

# Change options such that progress bar is not shown in the output file <- NEW!!!
  knitr::opts_knit$set(progress = FALSE, verbose = TRUE)

# libraries used in this Rmd
  library(ggplot2)
  library(tidyverse)
  library(flextable)
  library(gtsummary)
  library(knitr)
  
  library(cowplot)
```

```{r,  echo = FALSE, eval = TRUE}
# Load Rdata file
  filename <- list.files(path = "../Rdata/", pattern = "struma_prepared")

 load(file = paste0("../Rdata/", filename))
```

# Data manipulation

Work with data set 'iris'.

## Data manipulation - *group_by*

* **group_by**: allows you to group by a one or more variables
   - test it with 'Species'

\tiny

```{r, echo = TRUE, eval = TRUE}

```

## Data manipulation - *group_by* with *tally()*

- What happens if you add 'tally()' after having the data set grouped by 'Species'?

```{r, echo = TRUE, eval = TRUE}

```

## Data manipulation - *group_by* with *mutate()*

- Group by 'Species' and then calculate the mean of 'Sepal.Length'

\tiny
```{r, echo = TRUE, eval = TRUE}

```
 
## Data manipulation - *group_by* with *summarize()* 
 
* **summarize**: creates a new data.frame containing calculated summary information about a grouped variable

- group by 'Species'
- use 'summarize' to get information about
   + number of observations (hint: n())
   + mean of 'Sepal.Length' for each group
   + mean of 'Sepal.Width' for each group

\tiny
```{r, echo = TRUE, eval = TRUE}

```


## Data manipulation - *group_by* with *mutate()* and long format data
\tiny
```{r, echo = FALSE, eval = TRUE}
dt_example1 <-
  tibble(id = paste0("P", 1:4),
         sex = c("m", NA,"f","x"),
         weight_v1 = c(67, 63, 81, 88),
         weight_v2 = c(66, 71, 69, 88),
         weight_v3 = c(68, 65, 77, 90))

dt_example_long <-
  dt_example1 %>%
           select(id, sex, contains("weight")) %>% 
           pivot_longer(data = ., cols = -c(id, sex), names_to = "visit", names_prefix = "weight_", values_to = "weight") %>% 
  filter(!(id == "P2" & visit == "v3"))

dt_example_long 
```

- Can you calculate the mean weight for each patient?
- Can you calculate the difference to first weight measurement foreach patient?

```{r, echo = TRUE, eval = TRUE}

```
 

